---
title: "Wordpress: Convert Export to .csv"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: flatly
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```


# Workflow

## Export xml
First step is to export your Wordpress data, if you have not done so already: 
1. Logged into your account, in the left-navigation menu find "Export" under "Tools", and follow instructions to export and download (via email at the time of writing).
2. Extract the .zip download and identify your .xml file.

## Import to R-Studio

```{r,message=FALSE}
library(xml2)
library(tidyverse)
```

3. Set your working directory to that file location, and put your filename into the quotes below.

```{r}
filename <- "thoughtrepair.wordpress.2022-04-29.000.xml"
```

## One row per post 

The next step is to flatten the xml data structure into a rectangle with one post per line. The identifier of interest is "item". At this point we're throwing out any site-wide structure, and pages that are not posts.

```{r,  results = 'hide',message=FALSE}
df  <- read_xml(filename) %>% 
  as_list() %>% 
  tibble::as_tibble() %>%
  unnest_longer(rss)%>%
  dplyr::filter(rss_id == "item") %>%
  unnest_wider(rss) 

```

## Convert to df  

The resulting format is nearly final, but we need to specify the data of interest. Specifically, some aspect of the above process renders an unknown set of columns to be problematic. Here I have specified the columns of interest for my purposes, however you may want to inspect the dataframe at this point to get a sense of what columns you additionally need or don't. Regardless, given that your Wordpress posts are not mine, you may run into an error at this point. The following comment describes how I debugged it for my purposes, along with my impression of the error (without fully resolving it, generally).

*While I did not fully debug, I spent some time and will share the insight for those interested in pursuing this further. The issue seems to be between the non-uniform number of values for specific variables (such as comments) between articles, and the unnest_wider function. An alternative is that further unnesting is needed. In any case, the first column I had successfully identified as breaking the script given columns that were breaking it, was a `comment` column. Use that information how you will.* 

```{r, results = 'hide',message=FALSE}

df2  <- df %>%
  select(title,pubDate,creator,
         `encoded...7`,`encoded...8`,
         post_date,post_modified,
         link,post_type,
         status,post_parent,
         starts_with("category"),
         comment...32
  ) %>% 
  unnest(cols = names(.)) %>%
unnest(cols = names(.)) %>%
  readr::type_convert() 

```


At this point you have a dataframe appropriately structured with one line per post. 
```{r}
head(df2)
```

### Non-post content 
If you have additional content besides text-based posts, as I did, there will also be lines for those entities, such as captioned photos, technically "nested" within a post. 
I kept these, but you may not want to.
To remove them, selecting only parent items, something like this, should work: 
.
```{r eval = FALSE}
df <- filter(df, post_parent=="")
```

## Write to csv

```{r}
write_csv(df2,file="wordpress_posts.csv")
```

